---
title: "Powerful Pandas Project"
author: "Wonderful People"
date: "2025-12-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Research Questions

Primary: Conduct a binomial regression (hint: glm() function) to assess whether individuals with on-going health issues believe their condition will get worse while waiting for treatment.

Secondary: Assess the prevalence of health issues in the cohort (adjusting for other factors?).

Sample Validation: Assess how representative the sample is compared to the population.

## Data Cleaning
Put all data sets in Raw_Data folder and call your own data set H.csv

We had set of data. We binded the data by matching the column names and matching the values in each column.

```{r cars}
#This is our R script to clean data
final_data <- readRDS("Clean Data/final_Data.rds")
Data <- final_data

```

## Primary Question: Data Analysis


Then we created a non-adjusted regression model to see the effects of mental and physical health on beliefs. The code is as follows:

```{r pressure1}

#Fit the logistic regression model for PH and MH effect on belief, without adjustment
non_adjusted <- glm(Belief~MH+PH,data=Data,family="binomial")
coef_summary <- summary(non_adjusted)
coefficients <- coef(non_adjusted)
p_values <- coef_summary$coefficients[, "Pr(>|z|)"]
conf_int <- confint(non_adjusted)
summary(non_adjusted)
```

We see that MH is significant with a pval of `r p_values[2]`, decreasing belief, however, PH is not significant

Then we created a regression to see how an individuals physical health effects that belief. The code is as follows:


```{r pressure2}
adjusted <- glm(Belief~PH+MH+Age + factor(SES5),data=Data,family="binomial")
coef_summary <- summary(adjusted)
coefficients <- coef(adjusted)
p_values <- coef_summary$coefficients[, "Pr(>|z|)"]
conf_int <- confint(adjusted)
summary(adjusted)
```

After adjusting for age and SES, we find that MH is again significant in reducing belief with pval of `r p_values[3]`. Again PH is not significant and interestingly, the only significant SES5 level relative to L1 was L3, which reduced belied with a pval of `r p_values[6]`

Then we created a regression to see how an individuals overall health effects that belief. If a patient had either poor mental health or phsyical health, they were classified as poor health overall. The code is as follows:

```{r pressure3}
#hi
```
## Primary Question: Results

## Secondary Question: Data Analysis
```{r pressure4}
#prop.table(xtabs(~H$Physical))# prevalence of physical health alone 
#prop.table(xtabs(~H$Mental))# prevalence of mental health alone 
#prop.table(xtabs(~Physical+Mental,H))# prevalence of both MH and PH 
#prop.table(xtabs(~H$Belief))
```

## Secondary Question: Results

## Sample Validations
