---
title: "Powerful Pandas Project"
author: "Tenlea, Promise and Daniel"
date: "2025-12-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Research Questions

Primary: Conduct a binomial regression (hint: glm() function) to assess whether individuals with on-going health issues believe their condition will get worse while waiting for treatment.

Secondary: Assess the prevalence of health issues in the cohort (adjusting for other factors?).

Sample Validation: Assess how representative the sample is compared to the population.

## Data Cleaning

We had set of data. We binded the data by matching the column names and matching the values in each column.

```{r cars}
summary(cars)
```

## Primary Question: Data Analysis

To answer our primary question be conducted three different logistic regressions. First we fit our null model to the outcome of whether a patient believed their outcome would get worse.

```{r pressure}
#hi
```

Then we created a regression to see how an individuals mental health effects that belief. The code is as follows:

```{r pressure1}
#hi
```

Then we created a regression to see how an individuals physical health effects that belief. The code is as follows:


```{r pressure2}
#hi
```

Then we created a regression to see how an individuals overall health effects that belief. If a patient had either poor mental health or phsyical health, they were classified as poor health overall. The code is as follows:

```{r pressure3}
#hi
```
## Primary Question: Results

## Secondary Question: Data Analysis


## Secondary Question: Results

## Sample Validations